---
title: "Random OD Matrix Generation"
author: Jascha Grübel
institute: ETH Zürich
date: 2017-12-08
output: html_notebook
---

#Generate Random OD Matrix

This script generates a random OD matrix. The user can specify a ratio to define the sparseness of the resulting matrix. If the user specifies the odds between zeros and ones as 3:1 than around 25% of the possible connections between nodes will be present. The probability for each jump is completely random and cannot be influenced. 

This script allows you to specify the number of intermediate locations `numInter`, the number of origins `numOrig`, the number of destinations `numDest`, the odds of a zero in the matrix `oddsZero`, and the odds of a one in the matrix `oddsOne`.

## User defined variables
```{r}
numInter <- 4 #Number of Intermediate Locations
numOrig <- 2 #Number of Origins
numDest <- 2 #Number of Destinations
oddsZero <- 2 #Odds that a zero appears in the matrix
oddsOne <- 5 #Odds that a one3 appears in the matrix
```

## Computation
```{r}
r.dim.odm <- numInter+numDest
c.dim.odm <- numInter+numOrig
odm.r <- matrix(sample(c(rep(0,oddsZero),rep(1,oddsOne)),r.dim.odm*dim.odm, replace=TRUE),r.dim.odm,c.dim.odm)
rownames(odm.r) <- 0:(r.dim.odm-1)
colnames(odm.r) <- numOrig:(c.dim.odm+numDest-1)

set.seed(1913)
for(i in 1:r.dim.odm){
  num_edges <- sum(odm.r[i,])
  rand_nums <- runif(num_edges)
  rand_dist <- rand_nums/sum(rand_nums)
  odm.r[i,odm.r[i,]>0]<-rand_dist
}
```

## Saving and Visualisation
```{r}
write.table(odm.r,"odMatrix.csv",quote = FALSE, dec = ".", sep=";",col.names = NA)
as.data.frame(odm.r)
```
